Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-15 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
Methods: Open collaboration.

\section{methods}

@@

This work has been done as an open collaboration by using \url{nmrlipids.blogspot.fi}~\cite{nmrlipids}
as a communication platform.
The approach is inspired by the Polymath project~\cite{gowers09}, however there are some essential differences. 
The present approach was started by publishing a manuscript~\cite{ollila13} discussing the glycerol backbone and choline structures 
in a Berger based model (the most used molecular dynamics simulation model for lipid bilayers).
After publishing the initial manuscript, the open invitation for further contributions and discussion through the blog was presented.
All the scientific contributions are done publicly through the blog and all contributors were offered coauthorship
according to the guidelines defined in the beginning of the project~\cite{creditsPOST}.
The acception of authorship is based on the self-assesment of the authors' scientific contribution to the project.
The contributions from each author are summarized in the Supplementary Information. %(the location depends on the journal probably).

Almost all simulation data, including running parameters for reprocution and trajectories for further analysis, are collected
to the nmrlipids community in Zenodo file repository \url{https://zenodo.org/collection/user-nmrlipids}.
Thus, besides the main topic of this manuscript we present the most extensive available collection of simulations trajectories
for lipid bilayers, which opens up numerous possiblities for different analyses with much less effort than previously required.
Further information, e.g. scripts, figures and manuscript text files, are available in the GitHub 
organization \url{https://github.com/NMRlipids} \todo{I will not assign a doi yet. We can wait for the journal decision.}.

>>>>

\section{Methods}

@@

This work has been done as a fully open collaboration, using the \url{nmrlipids.blogspot.fi} blog~\cite{nmrlipids}
as a communication platform.
Our approach is inspired by the Polymath project~\cite{gowers09}, however there are some essential differences. 
We started by publishing a manuscript~\cite{ollila13} discussing the glycerol backbone and choline structures 
in a Berger-based model (the most used molecular dynamics simulation model for lipid bilayers).
Simultaneously,  we presented an open invitation for further contributions and discussion on the blog.
All the scientific contributions were made publicly through the blog. Every contributor was offered coauthorship
according to the guidelines defined in the beginning of the project~\cite{creditsPOST};
the acceptance of the offer was based on authors' self-assesment of their scientific contribution.
These contributions are summarized in the Supplementary Information. %(the location depends on the journal probably).

Almost all simulation data, including input files for reproduction and trajectories for further analysis, are collected
on our CERN-hosted Zenodo file repository (\url{https://zenodo.org/collection/user-nmrlipids}).
Thus, in addition to the main topic of this manuscript, we present the most extensive publicly available collection of simulation trajectories
for lipid bilayers, opening up numerous possiblities for different analyses with much less effort than previously required.
Further information, such as scripts, figures, and manuscript text files, are available through our GitHub 
repository (\url{https://github.com/NMRlipids}). \todo{I will not assign a doi yet. We can wait for the journal decision.}.
